Actuator line modeling of vertical-axis turbines

### 2016-05-12 paper.tex
Remove unused Mandal--Burton fc model details

The rotating blades of a cross-flow turbine will have non-constant chordwise
angle of attack distributions due to their circular paths---producing so-called
flow curvature effects~\cite{Migliore1980}. This makes it difficult to define a
single angle of attack for use in the static coefficient lookup tables.
Furthermore, this effect is more pronounced for high solidity ($c/R$) turbines.
Two different flow curvature corrections were considered: one derived in Goude
\cite{Goude2012} and one by Mandal and Burton \cite{Mandal1994}.

The Goude correction is derived by considering a flat plat moving along a
circular path in potential flow, for which the effective angle of attack
including flow curvature effects is given by
\begin{equation}
    \alpha = \delta + \arctan \frac{V_\mathrm{abs} \cos(\theta_b -
        \beta)}{V_\mathrm{abs} \sin(\theta_b - \beta) + \Omega R} - \frac{\Omega
        x_{0r}c}{V_\mathrm{ref}} - \frac{\Omega c}{4 V_\mathrm{ref}},
    \label{eq:Goude-curvature}
\end{equation}
where $\delta$ is the blade pitch angle, $V_\mathrm{abs}$ is the magnitude of
the local inflow velocity at the blade, $\theta_b$ is the blade azimuthal
position, $\beta$ is the direction of the inflow velocity, $\Omega$ is the
turbine's angular velocity, $R$ is the blade element radius, $x_{0r}$ is a
normalized blade attachment point along the chord (or fractional chord distance
of the mounting point from the quarter-chord), $c$ is the blade chord length,
and $V_\mathrm{ref}$ is the reference flow velocity for calculating angle of
attack.

@@

The Mandal--Burton flow curvature correction assumes that since the blade is
encountering a curvilinear flow, it can be treated as having virtual camber.
They introduce a factor to describe the variation of angle of attack from the
leading to trailing edge
\begin{equation}
    \Delta \alpha = \alpha_\mathrm{TE} - \alpha_\mathrm{LE},
    \label{eq:Mandal-Burton-alpha-diff}
\end{equation}
where TE and LE subscripts denote the values of angle of attack at the trailing
and leading edge, respectively. Calculating these values for an actuator line
element can be done by tracking the leading and trailing edge locations and
velocities, then performing the same vector arithmetic used to calculate the
quarter-chord angle of attack.

An incidence correction factor
\begin{equation}
    \alpha_c = \arctan \left( \frac{1 - \cos (\Delta \alpha / 2)}{\sin (\Delta
        \alpha / 2)} \right)
    \label{eq:Mandal-Burton-alpha-corr}
\end{equation}
is introduced and added to the uncorrected angle of attack. Like the Goude
model, $\alpha_c$ is positive on the upstream half of the turbine rotation and
negative on the downstream half.

It was determined that the Goude model performed best with respect to matching
the near-wake characteristics measured in the experiments, while the performance
predictions from both flow curvature models were relatively close to each other.
Thus, the Goude model was used for all simulations reported here.

>>>>

The rotating blades of a cross-flow turbine will have non-constant chordwise
angle of attack distributions due to their circular paths---producing so-called
flow curvature effects~\cite{Migliore1980}. This makes it difficult to define a
single angle of attack for use in the static coefficient lookup tables.
Furthermore, this effect is more pronounced for high solidity ($c/R$) turbines.

The flow curvature correction used here was derived in Goude \cite{Goude2012} by
considering a flat plat moving along a circular path in potential flow, for
which the effective angle of attack including flow curvature effects is given by
\begin{equation}
    \alpha = \delta + \arctan \frac{V_\mathrm{abs} \cos(\theta_b -
        \beta)}{V_\mathrm{abs} \sin(\theta_b - \beta) + \Omega R} - \frac{\Omega
        x_{0r}c}{V_\mathrm{ref}} - \frac{\Omega c}{4 V_\mathrm{ref}},
    \label{eq:Goude-curvature}
\end{equation}
where $\delta$ is the blade pitch angle, $V_\mathrm{abs}$ is the magnitude of
the local inflow velocity at the blade, $\theta_b$ is the blade azimuthal
position, $\beta$ is the direction of the inflow velocity, $\Omega$ is the
turbine's angular velocity, $R$ is the blade element radius, $x_{0r}$ is a
normalized blade attachment point along the chord (or fractional chord distance
of the mounting point from the quarter-chord), $c$ is the blade chord length,
and $V_\mathrm{ref}$ is the reference flow velocity for calculating angle of
attack.

@@
